Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-08-06 drafts/outline.tex
fairly minor edits

Because we assume the shape of the sediment profile follows the Rouse equation, which is time-invariant, proportionality between the average concentration and the concentration at a given height ($\phi_a$) can be assumed to remain constant: $\bar{\phi}=\frac{\phi_a}{C}$. The solution of the above differential equation, \[\bar{\phi}(t) = \bar{\phi}(0)e^{-kt}\,,\] relates $\bar{\phi}$ to its starting value, thus the proportionality constant is eliminated when $\phi_a$ is substituted: \[\phi_a(t) = \phi_a(0)e^{-kt}\,.\]

@@

\subsection{Turbulence Characterization Protocols}
Continuous velocity measurements were taken with an acoustic doppler velocimeter (ADV) at all points within our parameter space. At each point, velocity measurements were taken at 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting for at least 300 seconds. The ADV measured velocity, along with other data such as autocorrelation and signal-to-noise ratio, at a frequency of 10 Hz in the $x$, $y$, and two independent measures of data in the $z$ direction. Significant differences between these two measurements help inform data quality during post processing. The instrument was positioned within the flume so that with respect to flow, $x$ denoted the longitudinal direction, $y$ the transverse direction, and $z$ the vertical direction. Before each measurement, a mixture of walnut shell flour and tap water was released into the running flume, as the particulates were needed to act as a tracer in order for the ADV to accurately detect flow velocity.
%TODO

>>>>

Because we assume the shape of the sediment profile follows the Rouse equation, which is time-invariant, proportionality between the average concentration and the concentration at a given height ($\phi_a$) can be assumed to remain constant: $\bar{\phi}=\frac{\phi_a}{C}$. The solution of the above differential equation, 
\begin{equation}
    \bar{\phi}(t) = \bar{\phi}(0)e^{-kt}\,,
    \label{eq:avgconc}
\end{equation} 
relates $\bar{\phi}$ to its starting value, thus the proportionality constant $C$ is eliminated when $\phi_a$ is substituted: 
\begin{equation}
    \phi_a(t) = \phi_a(0)e^{-kt}\,.
    \label{eq:specconc}
\end{equation}

@@

\subsection{Turbulence Characterization Protocols}
Continuous velocity measurements were taken with an acoustic Doppler velocimeter (ADV) at all points within our parameter space. At each point, velocity measurements were taken at 6.7, 14.8, 24.9 and 36.1 cm above the flume bed, with each measurement lasting for at least 300 seconds. The ADV measured velocity, along with other data such as autocorrelation and signal-to-noise ratio, at a frequency of 10 Hz in the $x$, $y$, and two independent measures of data in the $z$ direction. Significant differences between these two measurements help inform data quality during post processing. The instrument was positioned within the flume so that with respect to flow, $x$ denoted the longitudinal direction, $y$ the transverse direction, and $z$ the vertical direction. Before each measurement, a mixture of walnut shell flour and tap water was released into the running flume, as the particulates were needed to act as a tracer in order for the ADV to accurately detect flow velocity.
%TODO
